---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

 <!-- badges: start -->
  [![R-CMD-check](https://github.com/harvard-ufds/saeczi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/harvard-ufds/saeczi/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->


## saeczi
#### (Small Area Estimation for Continous Zero Inflated data) 

`saeczi` is an R package that implements a small area estimator that uses a two-stage modeling approach for zero-inflated response variables. In particular, we are working with variables that follow a semi-continuous distribution with a mixture of zeroes and positive continuously distributed values. An example can be seen below:

```{r zi-plot, dpi = 300, fig.width = 5, fig.height=3, echo=F, message=F, warning=F}
set.seed(6)
library(tidyverse)

z <- tibble(
  z = rep(0, 2500)
)

nz <- tibble(
  nz = rgamma(1000, 3, 4)
)

ggplot() +
  geom_density(
    data = filter(nz, nz > 0.25),
    aes(x = nz, y = ..count..),
    fill = "#023047",
    color = "white",
    alpha = 0.9
    ) +
  geom_histogram(
    data = z,
    aes(x = z),
    fill = "#023047",
    color = "white",
    alpha = 0.9
    ) +
  labs(
    x = "Response Variable"
  ) +
  theme_bw()
```


`saeczi` first fits a linear mixed model to the non-zero portion of the response and then a generalized linear mixed model with binomial response to classify the probability of zero for a given data point. In estimation these models are each applied to new data points and combined to compute a final prediction. 

The package can also generate MSE estimates using a parametric bootstrap approach described in Chandra and Sud (2012) either in parallel or sequentially.

## Installation

You can install the developmental version of `saeczi` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("pak")
pak::pkg_install("harvard-ufds/saeczi")
```

## Example

We'll use the internal package datasets to show an example of how to use `saeczi`.

```{r, warning=FALSE, message=FALSE}
library(saeczi)
data(pop)
data(samp)

lin_formula <- DRYBIO_AG_TPA_live_ADJ ~ tcc16 + elev

set.seed(5)
result <- unit_zi(samp_dat = samp,
                  pop_dat = pop, 
                  lin_formula =  DRYBIO_AG_TPA_live_ADJ ~ tcc16 + elev,
                  log_formula = DRYBIO_AG_TPA_live_ADJ ~ tcc16 + elev,
                  domain_level = "COUNTYFIPS",
                  mse_est = TRUE,
                  B = 100,
                  parallel = FALSE)


result$res |> head()
```

