---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# saeczi

 <!-- badges: start -->
  [![R-CMD-check](https://github.com/harvard-ufds/saeczi/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/harvard-ufds/saeczi/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

# Development Mode

saeczi is still under development.  Please use at your own risk!  

# saeczi

saeczi is an R package that allows for the fitting of a zero-inflation estimator onto a sample dataset. Please note that, in order for a dataset to compatible with the zero-inflation estimator, the dataset must be of a sample dataset, where the means at the domain level of what would be considered a "population" dataset for the auxiliary variables must be available. To fit the zero-inflation estimator,first analyze the sample data and find a set of auxiliary variables that create a good model for both the linear regression model, as well as the logistic regression model. Lastly, assess the number of repetitions desired when fitting the bootstrap sample to estimate the variance. Once all of those things are decided, the unit_zi function can be used to predict domain level estimates of a sample dataset. 

## Installation

You can install saezi from github with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("harvard-ufds/saeczi")
```

